---
title: "Untitled"
author: "ManBuXiaoCun"
date: '2022-04-28'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library-in-nedd}
library(drc)
library(drcData)
library(boot)
library(lmtest)
library(metafor)
library(sandwich)
library(tidyverse)
```

Inhibitory eﬀect of secalonic acid on plant growth 
```{r}
plot1 <- ggplot(secalonic,aes(x=dose,y=rootl))+
  geom_point()+
  xlim(0,0.35)
plot1

plot2 <- plot1+scale_x_log10()
plot2
```

In weed science a four-parameter log-logistic model is often used to describe
dose-response relationships. We can use the model ﬁtting function **drm()**,
which is the pivotal function in the package drc for ﬁtting dose-response mod-
els.
```{r}
secalonic.LL.4 <- drm(rootl ~ dose,
data = secalonic,
fct = LL.4())
plot(secalonic.LL.4,
bp = 1e-3, broken = TRUE,
ylim = c(0, 7),
xlim = c(0, 0.35),
xlab = "Dose (mM)",
ylab = "Root length (cm)")
```
Replot by ggplot2 of secalonic.LL.4
```{r}
# ggplot()
```

Self choic of rootl ~ dose with **lm()**
The result is quite different from **drm()** function
```{r}
secalonic.lm <- lm(rootl ~ dose,data = secalonic)
```

